---
title: "Baseline Survey Final Results"
author: "University of Liberia School of Public Health Research Team" 
date: "2022-08-25"
output: 
  html_document:
    toc: true
    toc_depth: 3
    self_contained: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = here::here("outputs/figures/")
)

suppressPackageStartupMessages(source("packages.R"))
for (f in list.files(here::here("R"), full.names = TRUE)) source (f)

targets::tar_load(
  c(urban_montserrado, grand_bassa,
    urban_montserrado_int_grid, grand_bassa_int_grid,
    urban_montserrado_cmam_df, grand_bassa_cmam_df,
    urban_montserrado_cmam_int, grand_bassa_cmam_int,
    urban_montserrado_screening_df, grand_bassa_screening_df,
    urban_montserrado_screening_int, grand_bassa_screening_int,
    screening_estimates, screening_bootstraps,
    cmam_estimates, cmam_factors,
    urban_montserrado_vita_df, grand_bassa_vita_df,
    urban_montserrado_vita_int, grand_bassa_vita_int,
    vita_estimates, vita_bootstraps, vita_factors,
    urban_montserrado_mnp_df, grand_bassa_mnp_df,
    urban_montserrado_mnp_int, grand_bassa_mnp_int,
    mnp_estimates, mnp_bootstraps, mnp_factors,
    urban_montserrado_ifa_df, grand_bassa_ifa_df,
    urban_montserrado_ifa_int, grand_bassa_ifa_int,
    ifa_estimates, ifa_bootstraps, ifa_factors,
    urban_montserrado_icf_df, grand_bassa_icf_df,
    urban_montserrado_icf_int, grand_bassa_icf_int,
    icf_estimates, icf_bootstraps, icf_factors,
    urban_montserrado_anthro_df, grand_bassa_anthro_df,
    urban_montserrado_anthro_int, grand_bassa_anthro_int,
    wasting_bootstraps
  )
)

RdYlGn <- c("#d73027", "#fc8d59", "#fee08b", "#ffffbf", "#d9ef8b", "#91cf60", "#1a9850")

YlOrRd <- c("#ffffb2", "#fed976", "#feb24c", "#fd8d3c", "#fc4e2a", "#e31a1c",
"#b10026")

get_div_colours <- colorRampPalette(colors = RdYlGn, space = "Lab")
get_seq_colours <- colorRampPalette(colors = YlOrRd, space = "Lab")

col_palette <- get_div_colours(n = 101)
seq_palette <- get_seq_colours(n = 101)
```

<br/>

## Wasting prevalence

```{r wasting_table}
wasting_bootstraps |>
  dplyr::mutate(
    estimate_gm = scales::percent(estimate_gm, accuracy = 0.01),
    lcl_gm = scales::percent(lcl_gm, accuracy = 0.01),
    ucl_gm = scales::percent(ucl_gm, accuracy = 0.01),
    estimate_gb = scales::percent(estimate_gb, accuracy = 0.01),
    lcl_gb = scales::percent(lcl_gb, accuracy = 0.01),
    ucl_gb = scales::percent(ucl_gb, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", 
                  "Estimate", "95% LCL", "95% UCL", 
                  "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

### Global wasting

```{r wasting_maps1, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
x <- urban_montserrado_int_grid
x@data <- urban_montserrado_anthro_int * 100
x <- x |> sf::st_as_sf()

plot(
  x = x["gam"],
  main = NULL,
  pal = RColorBrewer::brewer.pal(n = 7, name = "YlOrRd"),
  nbreaks = 7,
  breaks = "quantile",
  key.pos = 4,
  lty = 0
)


y <- grand_bassa_int_grid
y@data <- grand_bassa_anthro_int * 100
y <- y |> sf::st_as_sf()

plot(
  x = y["gam"],
  main = NULL,
  pal = RColorBrewer::brewer.pal(n = 7, name = "YlOrRd"),
  nbreaks = 7,
  breaks = "quantile",
  key.pos = 4,
  lty = 0
)
```

### Moderate wasting

```{r wasting_maps2, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["mam"],
  main = NULL,
  pal = RColorBrewer::brewer.pal(n = 7, name = "YlOrRd"),
  nbreaks = 7,
  breaks = "quantile",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["mam"],
  main = NULL,
  pal = RColorBrewer::brewer.pal(n = 7, name = "YlOrRd"),
  nbreaks = 7,
  breaks = "quantile",
  key.pos = 4,
  lty = 0
)
```

### Severe wasting

```{r wasting_maps3, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["sam"],
  main = NULL,
  pal = RColorBrewer::brewer.pal(n = 7, name = "YlOrRd"),
  nbreaks = 7,
  breaks = "quantile",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["sam"],
  main = NULL,
  pal = RColorBrewer::brewer.pal(n = 7, name = "YlOrRd"),
  nbreaks = 7,
  breaks = "quantile",
  key.pos = 4,
  lty = 0
)
```

### Oedema

```{r wasting_maps4, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["oedema"],
  main = NULL,
  pal = RColorBrewer::brewer.pal(n = 7, name = "YlOrRd"),
  nbreaks = 7,
  breaks = "quantile",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["oedema"],
  main = NULL,
  pal = RColorBrewer::brewer.pal(n = 7, name = "YlOrRd"),
  nbreaks = 7,
  breaks = "quantile",
  key.pos = 4,
  lty = 0
)
```

## Anthropometric screening - MUAC

```{r muac_screening, fig.show = "hold", out.width = "50%"}
x <- urban_montserrado_int_grid
x@data <- urban_montserrado_screening_int * 100
x <- x |> sf::st_as_sf()

y <- grand_bassa_int_grid
y@data <- grand_bassa_screening_int * 100
y <- y |> sf::st_as_sf()

par(mar = c(0,0,0,0))

plot(
  x = x["muac_screen"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["muac_screen"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

## Anthropometric screening - oedema

```{r oedema_screening, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["oedema_screen"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["oedema_screen"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

```{r screening_table}
screening_bootstraps |>
  dplyr::mutate(
    estimate_gm = scales::percent(estimate_gm, accuracy = 0.01),
    lcl_gm = scales::percent(lcl_gm, accuracy = 0.01),
    ucl_gm = scales::percent(ucl_gm, accuracy = 0.01),
    estimate_gb = scales::percent(estimate_gb, accuracy = 0.01),
    lcl_gb = scales::percent(lcl_gb, accuracy = 0.01),
    ucl_gb = scales::percent(ucl_gb, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", 
                  "Estimate", "95% LCL", "95% UCL", 
                  "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

## CMAM Coverage

```{r}
cmam_estimates |>
    dplyr::mutate(
    estimate_gm = scales::percent(estimate_gm, accuracy = 0.01),
    lcl_gm = scales::percent(lcl_gm, accuracy = 0.01),
    ucl_gm = scales::percent(ucl_gm, accuracy = 0.01),
    estimate_gb = scales::percent(estimate_gb, accuracy = 0.01),
    lcl_gb = scales::percent(lcl_gb, accuracy = 0.01),
    ucl_gb = scales::percent(ucl_gb, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", 
                  "Estimate", "95% LCL", "95% UCL", 
                  "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

### Case-finding effectiveness

```{r case-finding, fig.show = "hold", out.width = "50%"}
x <- urban_montserrado_int_grid
x@data <- urban_montserrado_cmam_int * 100
x <- x |> sf::st_as_sf()

y <- grand_bassa_int_grid
y@data <- grand_bassa_cmam_int * 100
y <- y |> sf::st_as_sf()

par(mar = c(0,0,0,0))

plot(
  x = x["case_finding"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["case_finding"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Treatment coverage

```{r treatment, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["treatment"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["treatment"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Reasons for non-coverage

```{r out_reasons, fig.align = "center", fig.width = 12, fig.height = 8}
ggplot_pareto_factors(cmam_factors)
```

## Vitamin A supplementation coverage

```{r vita_coverage_map, fig.show = "hold", out.width = "50%"}
x <- urban_montserrado_int_grid
x@data <- urban_montserrado_vita_int * 100
x <- x |> sf::st_as_sf()

y <- grand_bassa_int_grid
y@data <- grand_bassa_vita_int * 100
y <- y |> sf::st_as_sf()

par(mar = c(0,0,0,0))

plot(
  x = x["vit1"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["vit1"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

```{r vita_coverage_table}
vita_bootstraps |>
  dplyr::mutate(
    estimate = scales::percent(estimate, accuracy = 0.01),
    lcl = scales::percent(lcl, accuracy = 0.01),
    ucl = scales::percent(ucl, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Area", "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  )
```

### Reasons for non-coverage

```{r vita_reasons, fig.align = "center", fig.width = 12, fig.height = 8}
ggplot_pareto_factors(vita_factors)
```

## Micronutrient powder supplementation coverage

```{r mnp_coverage_table}
mnp_bootstraps |>
  dplyr::mutate(
    estimate_gm = scales::percent(estimate_gm, accuracy = 0.01),
    lcl_gm = scales::percent(lcl_gm, accuracy = 0.01),
    ucl_gm = scales::percent(ucl_gm, accuracy = 0.01),
    estimate_gb = scales::percent(estimate_gb, accuracy = 0.01),
    lcl_gb = scales::percent(lcl_gb, accuracy = 0.01),
    ucl_gb = scales::percent(ucl_gb, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", "Estimate", "95% LCL", 
                  "95% UCL", "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

### Heard about micronutrient powder

```{r mnp1_coverage_map, fig.show = "hold", out.width = "50%"}
x <- urban_montserrado_int_grid
x@data <- urban_montserrado_mnp_int * 100
x <- x |> sf::st_as_sf()

y <- grand_bassa_int_grid
y@data <- grand_bassa_mnp_int * 100
y <- y |> sf::st_as_sf()

par(mar = c(0,0,0,0))

plot(
  x = x["mnp1"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["mnp1"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Received micronutrient powder

```{r mnp2_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["mnp2"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["mnp2"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Gave micronutrient powder to child

```{r mnp3_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["mnp3"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["mnp3"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Gave micronutrient powder to child at least 7 times in past week

```{r mnp4_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["mnp4"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["mnp4"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Reasons for non-coverage

```{r mnp_reasons, fig.align = "center", fig.width = 12, fig.height = 8}
ggplot_pareto_factors(mnp_factors)
```


## Iron-folic acid supplementation coverage

```{r ifa_coverage_table}
ifa_bootstraps |>
  dplyr::mutate(
    estimate_gm = scales::percent(estimate_gm, accuracy = 0.01),
    lcl_gm = scales::percent(lcl_gm, accuracy = 0.01),
    ucl_gm = scales::percent(ucl_gm, accuracy = 0.01),
    estimate_gb = scales::percent(estimate_gb, accuracy = 0.01),
    lcl_gb = scales::percent(lcl_gb, accuracy = 0.01),
    ucl_gb = scales::percent(ucl_gb, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", "Estimate", "95% LCL", 
                  "95% UCL", "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

### Attended antenatal care during pregnancy of youngest child

```{r ifa1_coverage_map, fig.show = "hold", out.width = "50%"}
x <- urban_montserrado_int_grid
x@data <- urban_montserrado_ifa_int * 100
x <- x |> sf::st_as_sf()

y <- grand_bassa_int_grid
y@data <- grand_bassa_ifa_int * 100
y <- y |> sf::st_as_sf()

par(mar = c(0,0,0,0))

plot(
  x = x["ifa1"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["ifa1"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Recieved information regarding iron-folic acid supplementation

```{r ifa2_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["ifa2"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["ifa2"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Recieved iron-folic acid tablets

```{r ifa3_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["ifa3"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["ifa3"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Consumed iron-folic acid tablets

```{r ifa4_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["ifa4"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["ifa4"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Consumed iron-folic acid tablets for at least 90 days

```{r ifa5_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["ifa5a"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["ifa5a"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Reasons for non-coverage

```{r ifa_reasons, fig.align = "center", fig.width = 12, fig.height = 8}
ggplot_pareto_factors(ifa_factors)
```

## IYCF counselling coverage

```{r icf_coverage_table}
icf_bootstraps |>
  dplyr::mutate(
    estimate_gm = scales::percent(estimate_gm, accuracy = 0.01),
    lcl_gm = scales::percent(lcl_gm, accuracy = 0.01),
    ucl_gm = scales::percent(ucl_gm, accuracy = 0.01),
    estimate_gb = scales::percent(estimate_gb, accuracy = 0.01),
    lcl_gb = scales::percent(lcl_gb, accuracy = 0.01),
    ucl_gb = scales::percent(ucl_gb, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", "Estimate", "95% LCL", 
                  "95% UCL", "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

### Heard about IYCF counselling

```{r icf1_coverage_map, fig.show = "hold", out.width = "50%"}
x <- urban_montserrado_int_grid
x@data <- urban_montserrado_icf_int * 100
x <- x |> sf::st_as_sf()

y <- grand_bassa_int_grid
y@data <- grand_bassa_icf_int * 100
y <- y |> sf::st_as_sf()

par(mar = c(0,0,0,0))

plot(
  x = x["icf1"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["icf1"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Attended IYCF counselling

```{r icf2_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot(
  x = x["icf2"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)

plot(
  x = y["icf2"],
  main = NULL,
  pal = col_palette,
  nbreaks = 101,
  breaks = "equal",
  key.pos = 4,
  lty = 0
)
```

### Reasons for non-coverage

```{r icf_reasons, fig.align = "center", fig.width = 12, fig.height = 8}
ggplot_pareto_factors(icf_factors)
```

<br/>
<br/>