---
title: "Baseline Survey Preliminary Results"
author: "University of Liberia School of Public Health Research Team" 
date: "2022-06-09"
output: 
  html_document:
    toc: true
    toc_depth: 3
    self_contained: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  echo = FALSE
)

suppressPackageStartupMessages(source("packages.R"))
for (f in list.files(here::here("R"), full.names = TRUE)) source (f)

targets::tar_load(
  c(urban_montserrado, grand_bassa,
    urban_montserrado_int_grid, grand_bassa_int_grid,
    urban_montserrado_cmam_df, grand_bassa_cmam_df,
    urban_montserrado_cmam_int, grand_bassa_cmam_int,
    urban_montserrado_screening_df, grand_bassa_screening_df,
    urban_montserrado_screening_int, grand_bassa_screening_int,
    screening_estimates, cmam_estimates, cmam_factors,
    urban_montserrado_vita_df, grand_bassa_vita_df,
    urban_montserrado_vita_int, grand_bassa_vita_int,
    vita_estimates, vita_factors,
    urban_montserrado_mnp_df, grand_bassa_mnp_df,
    urban_montserrado_mnp_int, grand_bassa_mnp_int,
    mnp_estimates, mnp_factors
  )
)

RdYlGn <- c("#d73027", "#fc8d59", "#fee08b", "#ffffbf", "#d9ef8b", "#91cf60", "#1a9850")

get_div_colours <- colorRampPalette(colors = RdYlGn, space = "Lab")

col_palette <- get_div_colours(n = 101)
```

<br/>

## Anthropometric screening - MUAC

```{r muac_screening, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_screening_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "muac_screen",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_screening_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "muac_screen",
  col_palette = col_palette
)
```

## Anthropometric screening - oedema

```{r oedema_screening, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_screening_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "oedema_screen",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_screening_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "oedema_screen",
  col_palette = col_palette
)
```

```{r screening_table}
screening_estimates |>
  dplyr::mutate(
    estimate_gm = scales::percent(estimate_gm, accuracy = 0.01),
    lcl_gm = scales::percent(lcl_gm, accuracy = 0.01),
    ucl_gm = scales::percent(ucl_gm, accuracy = 0.01),
    estimate_gb = scales::percent(estimate_gb, accuracy = 0.01),
    lcl_gb = scales::percent(lcl_gb, accuracy = 0.01),
    ucl_gb = scales::percent(ucl_gb, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", 
                  "Estimate", "95% LCL", "95% UCL", 
                  "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

## CMAM Coverage

```{r}
cmam_estimates |>
    dplyr::mutate(
    estimate_gm = scales::percent(estimate_gm, accuracy = 0.01),
    lcl_gm = scales::percent(lcl_gm, accuracy = 0.01),
    ucl_gm = scales::percent(ucl_gm, accuracy = 0.01),
    estimate_gb = scales::percent(estimate_gb, accuracy = 0.01),
    lcl_gb = scales::percent(lcl_gb, accuracy = 0.01),
    ucl_gb = scales::percent(ucl_gb, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", 
                  "Estimate", "95% LCL", "95% UCL", 
                  "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

### Case-finding effectiveness

```{r case-finding, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_cmam_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "case_finding",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_cmam_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "case_finding",
  col_palette = col_palette
)
```

### Treatment coverage

```{r treatment, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_cmam_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "treatment",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_cmam_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "treatment",
  col_palette = col_palette
)
```

### Reasons for non-coverage

```{r out_reasons, fig.align = "center", fig.width = 12, fig.height = 8}
ggplot_pareto_factors(cmam_factors)
```

## Vitamin A supplementation coverage

```{r vita_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_vita_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "vit1",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_vita_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "vit1",
  col_palette = col_palette
)
```

```{r vita_coverage_table}
vita_estimates |>
  dplyr::mutate(
    estimate = scales::percent(estimate, accuracy = 0.01),
    lcl = scales::percent(lcl, accuracy = 0.01),
    ucl = scales::percent(ucl, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Survey Area", "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  )
```

### Reasons for non-coverage

```{r vita_reasons, fig.align = "center", fig.width = 12, fig.height = 8}
ggplot_pareto_factors(vita_factors)
```

## Micronutrient powder supplementation coverage

```{r mnp_coverage_table}
mnp_estimates |>
  dplyr::mutate(
    gm_estimate = scales::percent(gm_estimate, accuracy = 0.01),
    gm_lcl = scales::percent(gm_lcl, accuracy = 0.01),
    gm_ucl = scales::percent(gm_ucl, accuracy = 0.01),
    gb_estimate = scales::percent(gb_estimate, accuracy = 0.01),
    gb_lcl = scales::percent(gb_lcl, accuracy = 0.01),
    gb_ucl = scales::percent(gb_ucl, accuracy = 0.01)
  ) |>
  knitr::kable(
    row.names = FALSE,
    col.names = c("Indicators", "Estimate", "95% LCL", 
                  "95% UCL", "Estimate", "95% LCL", "95% UCL"),
    align = "r"
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE,
    position = "center"
  ) |>
  kableExtra::add_header_above(
    header = c(" " = 1, "Urban Montserrado" = 3, "Grand Bassa" = 3),
    bold = TRUE
  )
```

### Heard about micronutrient powder

```{r mnp1_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_mnp_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "mnp1",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_mnp_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "mnp1",
  col_palette = col_palette
)
```

### Received micronutrient powder

```{r mnp2_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_mnp_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "mnp2",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_mnp_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "mnp2",
  col_palette = col_palette
)
```

### Gave micronutrient powder to child

```{r mnp3_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_mnp_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "mnp3",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_mnp_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "mnp3",
  col_palette = col_palette
)
```

### Gave micronutrient powder to child at least 7 times in past week

```{r mnp4_coverage_map, fig.show = "hold", out.width = "50%"}
par(mar = c(0,0,0,0))
plot_interpolation(
  interpolation = urban_montserrado_mnp_int,
  base_grid = urban_montserrado_int_grid,
  base_map = urban_montserrado,
  var = "mnp4",
  col_palette = col_palette
)

plot_interpolation(
  interpolation = grand_bassa_mnp_int,
  base_grid = grand_bassa_int_grid,
  base_map = grand_bassa,
  var = "mnp4",
  col_palette = col_palette
)
```

### Reasons for non-coverage

```{r mnp_reasons, fig.align = "center", fig.width = 12, fig.height = 8}
ggplot_pareto_factors(mnp_factors)
```



<br/>
<br/>