---
title: "Survey Progress Report"
author: "University of Liberia School of Public Health Research Team" 
date: '`r Sys.time()`'
output: 
  html_document:
    toc: true
    toc_depth: 3
    self_contained: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  echo = FALSE
)

suppressPackageStartupMessages(source("packages.R"))
for (f in list.files(here::here("R"), full.names = TRUE)) source (f)

targets::tar_load(
  c(
    team1_progress_table, team2_progress_table, team3_progress_table,
    team4_progress_table, team5_progress_table, team6_progress_table,
    team_progress_table,
    team1_overall_median_survey_time, team1_daily_median_survey_time,
    team2_overall_median_survey_time, team2_daily_median_survey_time,
    team3_overall_median_survey_time, team3_daily_median_survey_time,
    team4_overall_median_survey_time, team4_daily_median_survey_time,
    team5_overall_median_survey_time, team5_daily_median_survey_time,
    team6_overall_median_survey_time, team6_daily_median_survey_time,
    team_overall_median_survey_time, team_daily_median_survey_time
  )
)
```

<br/>

## Survey progress per team

```{r, eval = FALSE, fig.align = "center", fig.width = 16, fig.height = 30}
team_progress_table |>
  ggplot(mapping = aes(x = n, y = EFEACODE)) +
  geom_col() +
  facet_wrap(. ~ team, ncol = 1, scales = "free_y")
```

### Team 1

```{r, fig.align = "center", fig.height = 10}
team1_progress_table |>
  ggplot(mapping = aes(x = n, y = EFEACODE, fill = Date)) +
  geom_col(position = "stack", alpha = 0.7) +
  theme_minimal()
```

**Team 1 overall median survey time:** `r round(team1_overall_median_survey_time, 2)` minutes    
**Team 1 daily median survey time:** `r round(team1_daily_median_survey_time, 2)` minutes

### Team 2

```{r, fig.align = "center", fig.height = 10}
team2_progress_table |>
  ggplot(mapping = aes(x = n, y = EFEACODE, fill = Date)) +
  geom_col(position = "stack", alpha = 0.7) +
  theme_minimal()
```

**Team 2 overall median survey time:** `r round(team2_overall_median_survey_time, 2)` minutes    
**Team 2 daily median survey time:** `r round(team2_daily_median_survey_time, 2)` minutes

### Team 3

```{r, fig.align = "center", fig.height = 10}
team3_progress_table |>
  ggplot(mapping = aes(x = n, y = EFEACODE, fill = Date)) +
  geom_col(position = "stack", alpha = 0.7) +
  theme_minimal()
```

**Team 3 overall median survey time:** `r round(team3_overall_median_survey_time, 2)` minutes    
**Team 3 daily median survey time:** `r round(team3_daily_median_survey_time, 2)` minutes

### Team 4

```{r, fig.align = "center", fig.height = 10}
team4_progress_table |>
  ggplot(mapping = aes(x = n, y = EFEACODE, fill = Date)) +
  geom_col(position = "stack", alpha = 0.7) +
  theme_minimal()
```

**Team 4 overall median survey time:** `r round(team4_overall_median_survey_time, 2)` minutes    
**Team 4 daily median survey time:** `r round(team4_daily_median_survey_time, 2)` minutes

### Team 5

```{r, fig.align = "center", fig.height = 10}
team5_progress_table |>
  ggplot(mapping = aes(x = n, y = EFEACODE, fill = Date)) +
  geom_col(position = "stack", alpha = 0.7) +
  theme_minimal()
```

**Team 5 overall median survey time:** `r round(team5_overall_median_survey_time, 2)` minutes    
**Team 5 daily median survey time:** `r round(team5_daily_median_survey_time, 2)` minutes

### Team 6

```{r, fig.align = "center", fig.height = 10}
team6_progress_table |>
  ggplot(mapping = aes(x = n, y = EFEACODE, fill = Date)) +
  geom_col(position = "stack", alpha = 0.7) +
  theme_minimal()
```

**Team 6 overall median survey time:** `r round(team6_overall_median_survey_time, 2)` minutes    
**Team 6 daily median survey time:** `r round(team6_daily_median_survey_time, 2)` minutes

<br/>
<br/>